---
title: "Learning the `targets` package"
author: "Sophie Breitbart"
date: "February 2023"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

I used this tutorial: https://books.ropensci.org/targets/

# Set up project
## Set up data

Store original data in a folder I'd just call "data". Then make a copy, rename it to "data.csv", and put it in the root folder.

```{r echo=FALSE, warning=FALSE }
library(tidyverse)
```


```{r}
read.csv("data.csv") %>%
  head()
```

## Set up functions

Create a folder called "R" and, within that folder, make a script called "functions.R". This script will contain only functions. This package will carry out a pipeline by exclusively performing self-contained function after function.

## Set up _targets.R

Create an R script called "_targets.R" in the root folder. Use the same setup as the one in this project.


# Run this R script, "_targets.R"
This will always be in the root folder.
```{r warning=FALSE }
source("_targets.R")
```


# Useful things to do before running project

## Check pipeline is correct by getting info re: each target
```{r warning=FALSE }
tar_manifest(fields = all_of("command"))
```

## Visualize pipeline w/flow chart
Read from left to right.
```{r warning=FALSE }
tar_visnetwork()
```

# Run the pipeline
```{r}
tar_make()
```

# Review output
## Inspect plot
```{r warning=FALSE }
tar_read(plot)
```

## Reinspect flow chart pipeline and ask: is everything up to date?
```{r warning=FALSE}
tar_visnetwork()
```

```{r warning=FALSE }
tar_outdated()
```
